---
title: "Alcohol vs Seat choice"
author: "Melisha Wright"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Based on the box plot the back row consumes more alcohol than both the front and middle row.The median for the people that are in the back is higher than the top 75th percentile of the front seat and the middle seat people.      

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The mean for the people in the back seat is three times as much than the people in the middle seats and even more than the people in the front seats.  

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
since the p value from one way anova was such a small number we are going to follow up with a Tukey HSD test.
```{r}
plot(TukeyHSD(model1))
```

The middle back and front back confidence intervals are less than zero than the results would be significantly different.    

## Conclusions

The conclusion we made was most people in the back were drinking ther most alcohol because they had the highest mean in alcohol consumption. The middle row had the most people in it.


